A Constructive Ordered Predicate Logic for Category Theory

### 2022-10-07 paper/paper.tex
init the bib

Category theory is a branch of mathematics that gives a systematic
theory of typed, ``higher-dimensional'' algebraic structures.
%
Originally developed for applications to homological algebra, it was
quickly discovered that (among many other applications) these
categorical structures were common in logic and computer science, and
that formal systems like logics, type theories and programming
languages can be soundly and completely modeled
by notions of structured categories\cite{lawvere,goguen,lambek,moggi}, a
phenomenon sometimes referred to as the Curry-Howard-Lambek
nncorrespondence \cite{curry-howard-lambek}.
%
Examples include the simply typed lambda calculus \cite{lambekscott},
computational lambda calculus \cite{moggi}, linear logic \cite{girard}
and dependent type theory\cite{not-sure}.
%
These seminal works have led to a fruitful field of research known as
categorical logic, where new type theories are designed based directly
on category-theoretic semantics.
%
The slogan is that the syntax of a type theory should present an
initial object in its category of models, a category-theoretic
reformulation and generalization of the logical notion of soundness
and completeness.

>>>>

Category theory is a branch of mathematics that gives a systematic
theory of typed, ``higher-dimensional'' algebraic structures.
%
Originally developed for applications to homological algebra, it was
quickly discovered that (among many other applications) these
categorical structures were common in logic and computer science, and
that formal systems like logics, type theories and programming
languages can be soundly and completely modeled
by notions of structured categories\cite{lawvere,goguen,lambek,moggi}, a
phenomenon sometimes referred to as the Curry-Howard-Lambek
nncorrespondence \cite{curry-howard-lambek}.
%
Examples include the simply typed lambda calculus \cite{lambekscott},
computational lambda calculus \cite{moggi}, linear logic \cite{girard}
and dependent type theory\cite{cartmell1986}.
%
These seminal works have led to a fruitful field of research known as
categorical logic, where new type theories are designed based directly
on category-theoretic semantics.
%
The slogan is that the syntax of a type theory should present an
initial object in its category of models, a category-theoretic
reformulation and generalization of the logical notion of soundness
and completeness.
